Localisation and Sensor Privacy Using the Extended Information Filter and Secure Weighted Aggregation\thanksref{footnoteinfo}

### 2020-08-27 main.tex
Installed new banner plugin and updated banner comments making the subsection comments more identifiable
Clarified that our proof is in the random oracle model since the Joye-Libert one is Referred to multiple noise terms in our scheme (since the noise terms were introduced in the preliminaries section but not referenced) Fixed some inconsistencies in notation

%  .d8888b.                            888                 8888888b.                  888 d8b
% d88P  Y88b                           888                 888   Y88b                 888 Y8P
% 888    888                           888                 888    888                 888
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888
%                         888 888
%                    Y8b d88P 888
%                     "Y88P"  888
\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

% Quickly define homomorphic encryption and private aggregation here??

@@

@@

@@

%  .d8888b.                            888                 8888888b.                  888
% d88P  Y88b                           888                 888   Y88b                 888
% 888    888                           888                 888    888                 888
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  88888b.
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d88""88b 888 "88b
% 888    888 888     888  888 888  888 888   888  888      888        888    888  888 888  888
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y88..88P 888 d88P
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y88P"  88888P"
%                         888 888
%                    Y8b d88P 888
%                     "Y88P"  888
\section{Private Linear-Combination Aggregation}
For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation. In the context of navigation, $m$ weights $\omega_1^{(t)}, \dots , \omega_m^{(t)}$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$. This has been summarized in Figure \ref{fig:agg_steps}. In Section \ref{sec:private_localisation} we will show how this protocol is sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.

@@

% 888      .d8888b.        d8888  .d88888b.
% 888     d88P  Y88b      d88888 d88P" "Y88b
% 888     888    888     d88P888 888     888
% 888     888           d88P 888 888     888
% 888     888          d88P  888 888     888
% 888     888    888  d88P   888 888     888
% 888     Y88b  d88P d8888888888 Y88b. .d88P
% 88888888 "Y8888P" d88P     888  "Y88888P"

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

%  .d88888b.                                          888
% d88P" "Y88b                                         888
% 888     888                                         888
% 888     888 888  888 888d888      .d8888b   .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.
% 888     888 888  888 888P"        88K      d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b
% 888     888 888  888 888          "Y8888b. 888      888  888 88888888 888  888  888 88888888
% Y88b. .d88P Y88b 888 888               X88 Y88b.    888  888 Y8b.     888  888  888 Y8b.
%  "Y88888P"   "Y88888 888           88888P'  "Y8888P 888  888  "Y8888  888  888  888  "Y8888

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$.

@@

some summary here

\subsection{Proof}
To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.

@@

for some negligible functions $\eta_1$ and $\eta_2$. (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof.

@@

        for an unkonwn $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return

@@

% 888                            8888888b.                  888 d8b
% 888                            888   Y88b                 888 Y8P
% 888                            888    888                 888
% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.
% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b
% 888     888  888 888           888        888    88888888 888 888 888  888  888
% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888
% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888

>>>>

% 
%  .d8888b.                            888                 8888888b.                  888 d8b               
% d88P  Y88b                           888                 888   Y88b                 888 Y8P               
% 888    888                           888                 888    888                 888                   
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
% 888    888 888     888  888 888  888 888   888  888      888        888    88888888 888 888 888  888  888 
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y8b.     888 888 888  888  888 
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y8888  888 888 888  888  888 
%                         888 888                                                                           
%                    Y8b d88P 888                                                                           
%                     "Y88P"  888                                                                           
%

\section{Cryptography Preliminaries} \label{sec:crypto_prelim}
When defining our system security requirements and encryption scheme, we will reference some existing cryptographic security notions, the additively homomorphic Paillier encryption scheme, and the Joye-Libert private aggregation scheme.

% 
%  ######  ########  ######  ##     ## ########  #### ######## ##    ## 
% ##    ## ##       ##    ## ##     ## ##     ##  ##     ##     ##  ##  
% ##       ##       ##       ##     ## ##     ##  ##     ##      ####   
%  ######  ######   ##       ##     ## ########   ##     ##       ##    
%       ## ##       ##       ##     ## ##   ##    ##     ##       ##    
% ##    ## ##       ##    ## ##     ## ##    ##   ##     ##       ##    
%  ######  ########  ######   #######  ##     ## ####    ##       ##    
%

@@

% 
% ########     ###    #### ##       ##       #### ######## ########  
% ##     ##   ## ##    ##  ##       ##        ##  ##       ##     ## 
% ##     ##  ##   ##   ##  ##       ##        ##  ##       ##     ## 
% ########  ##     ##  ##  ##       ##        ##  ######   ########  
% ##        #########  ##  ##       ##        ##  ##       ##   ##   
% ##        ##     ##  ##  ##       ##        ##  ##       ##    ##  
% ##        ##     ## #### ######## ######## #### ######## ##     ## 
%

@@

% 
%       ##         ##    ## 
%       ##          ##  ##  
%       ##           ####   
%       ## #######    ##    
% ##    ##            ##    
% ##    ##            ##    
%  ######             ##    
%

@@

% 
%  .d8888b.                            888                 8888888b.                  888      
% d88P  Y88b                           888                 888   Y88b                 888      
% 888    888                           888                 888    888                 888      
% 888        888d888 888  888 88888b.  888888 .d88b.       888   d88P 888d888 .d88b.  88888b.  
% 888        888P"   888  888 888 "88b 888   d88""88b      8888888P"  888P"  d88""88b 888 "88b 
% 888    888 888     888  888 888  888 888   888  888      888        888    888  888 888  888 
% Y88b  d88P 888     Y88b 888 888 d88P Y88b. Y88..88P      888        888    Y88..88P 888 d88P 
%  "Y8888P"  888      "Y88888 88888P"   "Y888 "Y88P"       888        888     "Y88P"  88888P"  
%                         888 888                                                              
%                    Y8b d88P 888                                                              
%                     "Y88P"  888                                                              
%

\section{Private Linear-Combination Aggregation}
For achieving the goal of private localisation defined in Section \ref{sec:problem_statement} we will require a multi-party protocol for computing linear combinations of weights, and their subsequent aggregation. In the context of navigation, $m$ weights $\omega_j^{(t)}, 1 \leq j \leq m$ are first broadcast by the navigator, linear combinations $y^{(t)}_i=\sum^m_{j=1}x_{j,i}^{(t)}\omega_i^{(t)}$ are computed by each sensor $1\leq i\leq n$, and aggregation is computed back at the navigator, at every time step $t$. This has been summarized in Figure \ref{fig:agg_steps}. In Section \ref{sec:private_localisation} we will show how this protocol can be sufficient to compute measurement covariances and measurement vectors, and update the Extended Information Filter.

@@

% 
% ##        ######     ###     #######  
% ##       ##    ##   ## ##   ##     ## 
% ##       ##        ##   ##  ##     ## 
% ##       ##       ##     ## ##     ## 
% ##       ##       ######### ##     ## 
% ##       ##    ## ##     ## ##     ## 
% ########  ######  ##     ##  #######  
%

@@

\begin{description}
    \item[Setup] The challenger runs the $\mathsf{Setup}$ algorithm and gives $\mathsf{pub}$, $m$ and $pk_0$ to the attacker
    \item[Queries] The attacker can now perform encryptions or submit queries that are answered by the challenger. The types of actions are:
    \begin{enumerate}
        \item \textit{Encryption:} The attacker chooses a weight $\omega$ and computes an encryption of $\omega$ under the aggregator's public key $pk_0$, obtaining $\mathcal{E}_{pk_0}(\omega)$.
        \item \textit{Weight Queries:} The attacker chooses a time $t$ and receives the weights for that time encrypted with the aggregator's public key, $\mathcal{E}_{pk_0}(\omega^{(t)}_{j}),\,1\leq j\leq m$.
        \item \textit{Combine Queries:} The attacker chooses a tuple $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ such that for any two chosen combine query tuples $(i,t,x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$ and $(i',t',x^{\prime(t')}_{i',1},\dots,x^{\prime(t')}_{i',m})$, the following condition holds:
        \begin{equation*}
            i = i' \wedge t = t' \implies x^{(t)}_{i,m} = x^{\prime(t')}_{i',m},\,1\leq j\leq m\,.
        \end{equation*}
        They are given back the encryption of the linear combination $\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j)$ encrypted under both the aggregator public key $pk_0$ and the secret key $sk_i$.
        \item \textit{Compromise queries:} The attacker chooses $i$ and receives the secret key $sk_i$. The aggregator's secret key may also be compromised (when choosing $i=0$).
    \end{enumerate} 
    \item[Challenge] Next, the attacker chooses a time $t^*$, and a subset of users $S \subseteq U$ where $U$ is the complete set of users for which no combine queries, for time $t^*$, and no compromise queries, are made for the duration of the game. The attacker then chooses two series of tuples
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(0)}_{i,1},\dots,x^{(t^*)(0)}_{i,m})\,|\,i \in S\rangle
    \end{equation*}
    and
    \begin{equation*}
        \langle(i,t^*,x^{(t^*)(1)}_{i,1},\dots,x^{(t^*)(1)}_{i,m})\,|\, i \in S\rangle\,,
    \end{equation*}
    and gives them to the challenger. In the case that $0 \in S$ (\textit{i.e.} the aggregator is compromised) and $S = U$, it is additionally required that
    \begin{equation*}
        \sum_{i\in S}\sum^{m}_{j=1} x^{(t^*)(0)}_{i,j}\omega^{(t^*)}_j = \sum_{i \in S}\sum^{m}_{j=1} x^{(t^*)(1)}_{i,j}\omega^{(t^*)}_j\,,
    \end{equation*}
    for weights $\omega^{(t^*)}_j,\,1\leq j \leq m$ returned by a \textit{Weight Query} with chosen time $t^*$. The challenger then chooses a random bit $b \in \{1,0\}$ and returns encryptions 
    \begin{equation*}
        \langle\mathcal{E}_{pk_0,sk_i}(\sum^m_{j=1}x^{(t^*)(b)}_{i,j}\omega^{(t^*)}_j)\,|\,i\in U\rangle\,.
    \end{equation*}
    \item[More Queries] The attacker can now perform more encryptions and submit queries, so long as the queries do not break the requirements in the Challenge stage. That is, $S \subseteq U$.
    \item[Guess] At the end, the attacker outputs a bit $b'$ and wins the game only if $b' = b$. The advantage of an attacker $\mathcal{A}$ is defined as
    \begin{equation*}
        \mathsf{Adv}^{LCAO}(\mathcal{A}) \coloneqq \left\lvert \Pr [b'=b] - \frac{1}{2}\right\rvert\,.
    \end{equation*} 
\end{description}

@@

% 
%  .d88888b.                         .d8888b.           888                                      
% d88P" "Y88b                       d88P  Y88b          888                                      
% 888     888                       Y88b.               888                                      
% 888     888 888  888 888d888       "Y888b.    .d8888b 88888b.   .d88b.  88888b.d88b.   .d88b.  
% 888     888 888  888 888P"            "Y88b. d88P"    888 "88b d8P  Y8b 888 "888 "88b d8P  Y8b 
% 888     888 888  888 888                "888 888      888  888 88888888 888  888  888 88888888 
% Y88b. .d88P Y88b 888 888          Y88b  d88P Y88b.    888  888 Y8b.     888  888  888 Y8b.     
%  "Y88888P"   "Y88888 888           "Y8888P"   "Y8888P 888  888  "Y8888  888  888  888  "Y8888  
%                                                                                                
%                                                                                                
%                                                                                                
%

@@

    \item[$\mathsf{CombEnc}(t, pk_0, sk_i, \mathcal{E}_{pk_0}(\omega_1^{(t)}),\dots,\mathcal{E}_{pk_0}(\omega_m^{(t)}), x^{(t)}_{i,1},\dots,x^{(t)}_{i,m})$] The linear combination encryption step at time $t$ is computed as 
    \begin{equation}
        y^{(t)}_i = H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2}\,,
    \end{equation}
    and makes use of the homomorphic property \eqref{eqn:paillier_hom_mult}. Correctness follows from
    \begin{equation*}
        \begin{split}
             y^{(t)}_i &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(\omega^{(t)}_j)^{x^{(t)}_{i,j}} \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}\mathcal{E}_{pk_0}(x^{(t)}_{i,j}\omega^{(t)}_j) \pmod{N^2} \\
            &= H(t)^{sk_i}\prod^{m}_{j=1}(N+1)^{x^{(t)}_{i,j}\omega^{(t)}_j} r^{N}_{j} \pmod{N^2} \\
            &= H(t)^{sk_i}(N+1)^{\sum^{m}_{j=1}x^{(t)}_{i,j}\omega^{(t)}_j} r_{i}^{N} \pmod{N^2}\,,
        \end{split}
    \end{equation*}
    for some values $r_i,r_j \in \mathbb{Z}_N\,,1\leq j \leq m$. Here, $r_i^N$ and $H(t)^{sk_i}$ can be considered the noise terms corresponding to the two levels of encryption from $pk_0$ and $sk_i$, respectively.

@@

% 
% ########  ########   #######   #######  ######## 
% ##     ## ##     ## ##     ## ##     ## ##       
% ##     ## ##     ## ##     ## ##     ## ##       
% ########  ########  ##     ## ##     ## ######   
% ##        ##   ##   ##     ## ##     ## ##       
% ##        ##    ##  ##     ## ##     ## ##       
% ##        ##     ##  #######   #######  ##       
%

\subsection{Security Proof}
To prove the security of our introduced scheme, we recall the desired security properties of an LCAO secure scheme with IND-CPA secure encrypted weights. From the definition above, weights encrypted with public key $pk_0$ are identical to encryptions of the Paillier scheme, and therefore meet security notion IND-CPA. We omit this proof here and refer readers to the security proof of the Paillier encryption scheme \cite{paillierPublicKeyCryptosystemsBased1999} instead.

@@

for some negligible functions $\eta_1$ and $\eta_2$. (\textit{i.e.} if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure.) This is a contradiction to the Joye-Libert AO proof in \cite{joyeScalableSchemePrivacyPreserving2013}, and will thus conclude our proof. The function $H$ used by our scheme is treated as a \textit{random oracle} in the Joye-Libert AO proof and will, therefore, prove our scheme secure in the random oracle model as well.

@@

        for an unknown $b \in \{0,1\}$. Multiply series elements by $r_i^N,\,1 \leq i \leq n$ for randomly chosen $r_i \in \mathbb{Z}_N$ and return

@@

% 
% 888                            8888888b.                  888 d8b               
% 888                            888   Y88b                 888 Y8P               
% 888                            888    888                 888                   
% 888      .d88b.   .d8888b      888   d88P 888d888 .d88b.  888 888 88888b.d88b.  
% 888     d88""88b d88P"         8888888P"  888P"  d8P  Y8b 888 888 888 "888 "88b 
% 888     888  888 888           888        888    88888888 888 888 888  888  888 
% 888     Y88..88P Y88b.         888        888    Y8b.     888 888 888  888  888 
% 88888888 "Y88P"   "Y8888P      888        888     "Y8888  888 888 888  888  888 
%                                                                                 
%                                                                                 
%                                                                                 
%
